Climate control for performant HPUs

### 2014-04-10 docs/draft/draft1.tex
add compound f1score plot, update manuscript

\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{algorithm2e}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{framed, color}
\usepackage{color, soul}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\definecolor{blu}{rgb}{0,0,1}
\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
\newcommand{\vwm}{$V_{w,n,k}$}
\newcommand{\wm}{$W_{w,n,k}$}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}

@@

We paid 900 AMT workers to perform an image-labelling task.  A task consisted 
of labelling 10 images, with 5 labels each.  The first 5 images were varied 
depending on the priming treatment, while the last 5 images were the same 
accross all treatments.  Ordering of the images was kept constant.

@@

The 5 test images, were chosen carefully with two ideals in mind.  
First, we chose images that we judged would generate a diverse vocabulary of 
labels, such that the effects of priming could be detected.  In other words,
sparse images with a single object in the foreground were not considered good 
candidates, since they would be less likely to elicit labels that varied from 
one worker and one priming treatment to the next.

@@

Under these considerations, we chose the images shown in 
Fig.~\ref{fig:testImages}

\begin{figure*}
	\includegraphics[scale=1.00]{../figs/testImages.png}
	\label{fig:testImages}
\end{figure*}

\begin{figure*}
	\includegraphics[scale=1.00]{../figs/ambiguous.png}
	\label{fig:ambiguous}
\end{figure*}

\begin{figure*}
	\includegraphics[scale=1.00]{../figs/cultural.png}
	\label{fig:cultural}
\end{figure*}

\begin{figure*}
	\includegraphics[scale=1.00]{../figs/ingredients.png}
	\label{fig:ingredients}
\end{figure*}

We chose the three sets of priming images to that end.  The first set, was 
chosen to be 
for the treatment

\textit{culture}, and \textit{food}.
\section*{Results}
\begin{figure*}
	\includegraphics[scale=0.65]{../figs/specificity.pdf}
\end{figure*}

>>>>

\usepackage{fixltx2e}
\usepackage{tikz}
\usetikzlibrary{calc}
\usepackage{algorithm2e}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{cite}
\usepackage{framed, color}
\usepackage{color, soul}
\definecolor{shadecolor}{rgb}{.93,.93,.93}
\definecolor{blu}{rgb}{0,0,1}
\newcommand{\td}[1]{{\color{blu}\hl{TODO: #1}}}
\newcommand{\vwm}{$V_{w,n,k}$}
\newcommand{\wm}{$W_{w,n,k}$}
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{gensymb}

@@

\textbf{Task set-up.}
We paid 900 AMT workers to perform an image-labelling task.  A task consisted 
of labelling 10 images, with 5 labels each.  The first 5 images were varied 
depending on the priming treatment, while the last 5 images were the same 
accross all treatments.  Ordering of the images was kept constant.

@@

Tasks were presented to workers as a series of panels or flash cards.  The
first panel provided brief instructions, and was identical for all treatments.
Workers could see this panel when previewing the task, but could not advance.
Depending on the treatment, the worker was either shown a second pannel 
stating the name of 
one of two fictitious organizations funding the work, or this panel was 
skipped.  The next five pannels each consisting of a priming sub-tasks, 
wherein the worker was asked to submit five descriptive labels.  The images
used during the priming sub-task depended on the treatment.  The last 5 pannels
consisted of testing subtasks, wherein, as for the priming sub-tasks, workers
were asked to submit 5 descriptive labels.

\textbf{Choice of images.}
The 5 test images, were chosen with two ideals in mind.  
First, we chose images that we judged would generate a diverse vocabulary of 
labels, such that the effects of priming could be detected.  In other words,
sparse images with a single object in the foreground were not considered good 
candidates, since they would be less likely to elicit labels that varied from 
one worker and one priming treatment to the next.

@@

Under these considerations, we chose the images shown in 
Fig.~\ref{fig:testImages}.  Each of these images has food as its main focus,
but also has a strong and specific cultural reference due to the unique, 
iconic character of the food and the artifacts depicted.

To investigate in-task priming, we chose a set of images that highly
recognizeable cultural settings and no food, and another set that contained
separated food ingredients, without any overt cultural content.  The third
set of images was chosen to be very much like the test images, showing prepared
meals, and though prepared food is inseperable from culture, these images
were chosen based on being culturally more muted or ambiguous.

\textbf{Label ontology.}
In order to provide a deeper analysis, we built an ontology
of the corpus of all labels applied to the first test image.  The ontology
was built as a directed acyclic graph starting

\section*{Results and discussion}

\subsection*{Priming affects HPU output.}
Before looking for differences in the content of labels provided by workers
from different treatments, we first demonstrate that each treatment has a
distinguishable impact on worker output relative to the \textsc{ambg}.

Using a naive bayes classifier, we are able to distinguish with high precision
and specificity between workers from the \textsc{ambg} treatment and any of
the other 5 treatments.  Fig~\ref{fig:classifier} shows F1-score for a
naive bayes classifier when distinguishing between the \textsc{ambg} and 
target treatments. The classifier was trained using random subsamples of 
output 80 HPUs drawn from each of the \textsc{ambg} and target treatments, and
tested on the ouput of 20 HPUs from each treatment.

We find it remarkable that, using only the labels that workers provide, it is
possible to infer with good accuracy the treatment to which the worker was 
subjected.

\begin{figure*}
	\includegraphics[scale=0.65]{../figs/f1scores.pdf}
	\caption{caption here}
	\label{fig:classifier}
\end{figure*}

A natural question is to test the ability for the classifier to perform 
distinguish between other pairings of treatments.  For example, can the 
classifier distinguish $\textsc{cult}_{img}$ workers from 
$\textsc{cult}_{fund}$ workers?

% Graphics commented out because they make compiling take long!  
% Uncomment when desired!
\begin{figure*}
%	\includegraphics[scale=1.00]{../figs/testImages.png}
	\caption{caption here}
	\label{fig:testImages}
\end{figure*}

\begin{figure*}
%	\includegraphics[scale=1.00]{../figs/ambiguous.png}
	\caption{caption here}
	\label{fig:ambiguous}
\end{figure*}

\begin{figure*}
%	\includegraphics[scale=1.00]{../figs/cultural.png}
	\caption{caption here}
	\label{fig:cultural}
\end{figure*}

\begin{figure*}
%	\includegraphics[scale=1.00]{../figs/ingredients.png}
	\caption{caption here}
	\label{fig:ingredients}
\end{figure*}

\section*{Results}
\begin{figure*}
	\includegraphics[scale=0.65]{../figs/specificity2.pdf}
\end{figure*}
